\begin{rubric}{Experience}
\entry*[\textbf{2018.6 -- now}]%
	\textbf{VMware,Inc.\qquad Quality Reporter}%
\text{\qquad  Responsible for design and implementation Quality Reporter.}\par
\text{\qquad This tool can not only automatic collect and analysis data, but also update and generate reports, and email \par \qquad to responsible team.}\par
\entry*[\textbf{2018.1 -- 2018.5}]%
	\textbf{State Grid Cooperation of China \qquad Linux Patch Automatic Management System}%
\text{\qquad Acting as project leader.}\par
\text{\qquad Responsible for pre-project research, system technical architecture, system deployment architecture and \par \qquad the secure transfer scheme between the patch files and the internal and external networks.}
\entry*[\textbf{2017.2 -- 2017.10}]%
	\textbf{China Information Technology Security Evaluation Center}
\entry*[\textbf{2017.2 -- 2017.10}]%
    \textbf{Vulnerability Elimination and Control}%
\text{\qquad Acting as project leader.}\par
\text{\qquad Responsible for building OpenStack cloud platform, making QCOW2 format virtual machine.}\par
\text{\qquad Responsible for verifying vulnerabilities in operating systems, applications, and mobiles.}
\entry*[\textbf{2016.11 -- 2017.3}]%
	\textbf{Sichuan Changhong,Inc. \qquad Automatic Vulnerability Detection Tool}%
\text{\qquad Responsible for the design, implementation and testing of sensitive directory detection, weak password \par\qquad vulnerabilities, and CSRF vulnerability scanning tools}
\entry*[\textbf{2016.4 -- 2017.2}]%
	\textbf{Beijing Ruian,Inc. \qquad Internet Application Analysis and Development}%
\text{\qquad Responsible for the protocol analysis of the PC and Android clients, independently wrote and delivered \par\qquad the protocol analysis report, and completed the development of the corresponding HTTP template.}\par
\end{rubric}